% The .tex file designed by Dr. Hardepp Singh Rai, (Dean, Testing and Consultancy, Guru Nanak Dev Engineering College, Ludhiana, Punjab), Dr. Jaiteg Singh Khaira (Professr, Chitakara Unviersity, Punjab) and Er. Sukhjit Singh Sehra(Asst Prof, Guru Nanak Dev Engineering College, Ludhiana, Punjab). It has been specifically designed for Students of PG and PhD Scholars of Chitkara University. 
\chapter*{\protect\centerline{ACKNOWLEDGEMENT }} 

% \rule{29em}{0.8pt}\\[6pt]}


\noindent I am highly grateful to \textbf{Dr. Ashok Chitkara}, CHANCELLOR and \textbf{Dr. Madhu Chitkara}, VICE-CHANCELLOR, Chitkara University, for providing opportunity to carry out this thesis work.

The constant guidance and encouragement received from my supervisor \textbf{\guidenames}, \designationname, \guidedepartmentname, has been of great help in carrying out the present work and is acknowledged with reverential thanks. Without the wise counsel and able guidance, it would have been impossible to complete the thesis in this manner.

I would like to express thanks profusely to \textbf{XXX-XXX }, Associate Professor \& Head (Computer Science \& Engineering) for stimulating me time to time. I would also like to thank \textbf{ XXX-XXX}, Head of Department (Information Technology) and to entire faculty, staff of Computer Science \& Engineering Department. I also thanks my friends who devoted their valuable time and helped me in all possible ways towards successful completion of this work. 

I am also thankful to the authors whose works I have consulted and quoted in my thesis work. Lastly, I would also like to thank my parents for their years of unyielding love and encouragement. I will always admire their determination and sacrifice during my thesis work.


\vspace*{0.3in}
\begin{flushright}
\textbf{(\studentname)}
\end{flushright}
