\chapter{Introduction to Organisation}\hrule
\label{Chapter:1}
% =====================================================================================================
\section {Organisation Profile and Hisotry}
I am having my Six Weeks Training at Testing And Consultancy Cell at Guru Nanak Dev
Engineering College Ludhiana. Guru Nanak Dev Engineering College was established by the
Nankana Sahib Education Trust (NSET) Ludhiana. The Nankana Sahib Education Trust (NSET)
was founded in the memory of the most sacred temple of Sri Nankana Sahib, birth place of Sri Guru
Nanak Dev Ji. With the mission of ``Removal of Economic Backwardness through Technology''
Shiromani Gurudwara Parbandhak Committee (SGPC) started a Polytechnical in 1953 and an
Engineering College in 1956.\\
\\
NSET resolved to uplift Rural areas by admitting 70\% of students from these rural areas every year.
This committent was made to nation on 8th April, 1956, the day foundation stone of the college
building was laid by Dr. Rajendra Prasad Ji, the First President of India. The College is now ISO
9001:2000 certified.\\
\\
Guru Nanak Dev Engineering College campus is spread over 88 acres of prime land about 5 Kms
from Bus Stand and 8 Kms from Ludhiana Railway Station on Ludhiana - Malerkotla Road. The
college campus is well planned with beautifully laid out tree plantation, pathways, flowerbeds
besides the well maintained sprawling lawns all around. It has beautiful building for College,
Hostels, Swimming Pool, Sports and Gymnasium Hall Complex, Gurudwara Sahib, Bank,
Dispensary, Post Office etc. There are two hostels for boys and one for girls with total
accommodation of about 550 students. The main goal of this institute is :
\begin{itemize}
	\item To build \& promote teams of experts in the upcoming specialisations
	\item To promote quality research and undertake research projects keeping in view their
	relevance to needs and requirements of technology in local industry.
	\item To start on-line transfer of knowledge in appropriate technology by means of establishing
	multi-purpose resource centres.
\end{itemize}
