\documentclass[11pt,a4paper]{article}
\author{H.S.Rai, J. Singh and S.S. Sehra}
\title{Exercises for Third Lab}
%\date{20th, January, 2016}
%\renewcommand{\familydefault}{\rmdefault}
%\renewcommand\rmdefault{ptm}
%\renewcommand{\familydefault}{\ttdefault}
\begin{document}
\maketitle


We welcome you to the  first lab session of workshop. Following are the instructions for running various exercises to be executed using \LaTeX\ GUI \TeX studio. You can download the folder of "Thesis" and paper template from bitbucket account when you are asked to do so.

The process for generating PDF is to click green button under menu bar on \TeX studio, then goto ``Tools'' and click on bibliography (Bib\TeX) and again do pdflatex two times. Right hand side window will  show the output pdf generated. If the cross reference has not appeared then try to do pdflatex one more time and if bibliography still not in the desired format, please repeat the process. Below is the list of exercise you have to perform..

\section{JabRef}
\begin{enumerate}

\item Understanding JabRef
\item Building Database by Manual Entry 
\item Import Bibliographic Database
\item Adding database using search through various databases 
\item Attaching pdf files to entries
\item Creating groups
\item Creating abbreviations
\item Generating keys
\item Removing Duplicate entries
\item Searching Database
\item Retrieving References in a Database

\end{enumerate}

\section{Working with Bib\TeX\ and Natbib}
\begin{itemize}
\item Exporting database in \LaTeX.
\item Working with Bib\TeX.
\item Natbib and its numbers and author year styles.

\end{itemize}

\section{Reference Management of Thesis/Research Papers}
\begin{enumerate}
\item Working with its references 
\item Working with papers and changing styles. 
\end{enumerate}

\end{document}
