\documentclass[11pt,a4paper]{article}
\author{H.S. Rai, J. Singh and S.S.Sehra}
\title{Exercises for 12th March, 2016}
\date{}
\begin{document}
\maketitle
Dear Participants,

We welcome you to the  first lab session of workshop. Following are the instructions for running various exercises to be executed using \LaTeX\ GUI \TeX studio. A folder of exercises would be provided to you. The folder contains list of exercises based on different section and each section further have folders for individual exercise. In each exercise there are two parts:
\begin{enumerate}
\item  Tasks to be performed.
\item Demonstration of the syntax
\end{enumerate}

The process for generating PDF is to click green button under menu bar on \TeX studio. Once you click it and do pdflatex, right hand side window will  show the output pdf generated. If the cross reference has not appeared then try to do pdflatex one more time. Below is the list of exercise you have to perform.

 
\section{Creating a Document}
 \begin{enumerate}
 \item First \LaTeX\ Document.
 \item Handling preamble of the Document, abstract, Comments, and displaying the title of your document. 
 \item Basic Formatting
 
% \item Basic formatting:  create new paragraphs and new lines, paragraph Alignment (Text Justification), Paragraph Indentation. 
% \item Creating Bold, italics and underlining text.
 \end{enumerate}
\section{Lists}
 \begin{enumerate}
 \item Creating Unordered list.
 \item Creating Ordered lists.
 \item Creating Nested Lists.
 \end{enumerate}
 \section{Document Structure}
 \begin{enumerate}
 \item Creating parts, Chapters, sections, subsections.
 \item Creating Numbered and unnumbered parts, Chapters, sections.
 \item Working with Glossaries, Nomenclature and index
 \item Creating Hyperlinks in the document and Linking web addresses.
 \item Inserting Footnotes in Documents
 \item Managing Table of contents of document.
 \end{enumerate}
\section{Figures}
 \begin{enumerate}
 \item Inserting figures in the document.
 \item Creating captions, Labels and cross-references.
 \item Scaling Images and rotating images.
 \end{enumerate}
 
 \section{Tables}
  \begin{enumerate}
  \item Creating tables in the document with variable width.
   \item Creating tables in the document with fixed width.
  \item Creating captions, Labels and cross-references.
  \item Creating multi-row and multi-column tables.
  \end{enumerate}

\section{Page Formatting}
 \begin{enumerate}
 \item Creating Headers and Footers of your document
 \item Creating and changing page numbering.
 \item Managing paragraph spacing 
 \item Creating multiple columns style
 \item Displaying Code Content using verbatim environment
 \end{enumerate}
\section{Mathematics}
\begin{enumerate}
\item Inserting Math equation in the Document.
\item Create equation numbering and cross referencing it.
\item Create equations using fractions

\section{Working with Large Files}
\begin{enumerate}
\item Splitting file into folders
\item Working with thesis. inserting all components of thesis
\end{enumerate}

\section{Generating Research Papers}
\begin{enumerate}

\item Working with papers and changing styles. 
\end{enumerate}


\end{enumerate}
\end{document}
